Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
Related work also in IX

The centrality of the functional abstraction and its security are behind the
many software and hardware mechanisms proposed for its protection
\cite{Cowan+98, NagarakatteZMZ09, NagarakatteZMZ10, DeviettiBMZ08,
Kuznetsov+14, Dang+15, Shanbhogue+19, Woodruff+14, Chisnall+15,
SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises,
DBLP:conf/sp/RoesslerD18, Gollapudi+23}, which we survey briefly in
\cref{sec:intro}. Among these techniques, the micro-policies of Roessler and
DeHon \cite{DBLP:conf/sp/RoesslerD18} are the most flexible in supporting a
range of safeguards including lazy enforcement, and suitable for formulating
and validating strong security guarantees.

@@

Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{DBLP:conf/sp/WatsonWNMACDDGL15}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has uses these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{SkorstengaardLocal,SkorstengaardSTKJFP,Georges22:TempsDesCerises}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.

>>>>

The centrality of the functional abstraction and its security are behind the
many software and hardware mechanisms proposed for its protection
\cite{Cowan+98, NagarakatteZMZ09, NagarakatteZMZ10, DeviettiBMZ08,
Kuznetsov+14, Dang+15, Shanbhogue+19, Woodruff+14, Chisnall+15,
SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises,
DBLP:conf/sp/RoesslerD18, Gollapudi+23}, which we survey in
Sections~\ref{sec:intro} and~\ref{sec:future}. Among these techniques, the micro-policies of Roessler and
DeHon \cite{DBLP:conf/sp/RoesslerD18} are the most flexible in supporting a
range of safeguards including lazy enforcement, and suitable for formulating
and validating strong security guarantees.

@@

Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{DBLP:conf/sp/WatsonWNMACDDGL15}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has used these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{SkorstengaardLocal,SkorstengaardSTKJFP,Georges22:TempsDesCerises}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.
